\newpage
\chapter*{Abstract}
With the digitalization any historical record are available in the form of collection of bits. Any document can be stored in advanced electronic devices like computers, smart phones file systems as files. The most used or popular files are media files (image, audio, video). For the lack of true information and experience or bad ethics of mind the number of digital scams is getting higher in developing country like India. So the data files need to be protected somehow somewhere and also there should be a system that will veryfy the requested file. So we started with the simplest media format \textit{i.e.} Image. Making a centrral database can be unreliable because the system can be breached and the data might be changed no matter how advanced and protective the protocols are. So we took the concept from advanced decentralized architecture of BlockChain mostly BitCoin.
A purely peer-to-peer version of online data would allow online transactions to be sent directly from one node to another without going through a central authority. Digital signatures provide part of the solution.
The network timestamps transactions by hashing them into an ongoing chain of hash-based proof-of-work, forming a record that cannot be changed without redoing the proof-of-work. The longest chain not only serves as proof of the sequence of events witnessed, but proof that it came from the largest pool of CPU power. As long as a majority of CPU power is controlled by nodes that are not cooperating to attack the network, they'll generate the longest chain and outpace attackers. The network itself requires minimal structure. Messages are broadcast on a best effort basis, and nodes can leave and rejoin the network at will, accepting the longest proof-of-work chain as proof of what happened while they were gone.
To prevent the action against one of the biggest issues in India of Fake Media (Image, Sound) Scam. This project tries to find a way to prevent it with a new upcoming technology starting with image files.

\textbf{Keywords:} Peer-to-Peer network, Proof-of-work, Proof-of-Stake, Distributed Ledger, Concensus Mechanism, Hash Function, Video Formatting, Image File formats, Watermarking, WebServer.
